% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 

\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage[hidelinks]{hyperref}
\usepackage{color}

\definecolor{background-gray}{gray}{0.3}
\definecolor{text-white}{gray}{.9}
\definecolor{text-gray}{gray}{.2}

\color{text-gray}
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 
\resumewidth=5.5in
\sectionwidth=.5in
\newcommand{\headercorrection}{.55in}
\voffset=-.25in


\begin{document} 
\hspace*{-\headercorrection}{
	\bf
	{\Huge Samuel P. Rogal }\\
	\hspace*{-\headercorrection}{
		\colorbox{background-gray}{
			\strut \color{text-white} Web Developer
			\hspace{\linewidth}\hspace{-16\fboxsep}
		}
	}
}\\

\vspace{-0.5in}	

\begin{flushleft}
 	\footnotesize \input{contact}
\end{flushleft}
        
\vspace{-0.3in}	                                  
\begin{resume}


\section{ABSTRACT}          
    I enjoy having a variety of work, and my most recent experience takes the cake for "Full Stack". \\
    	Generally working on my own, I...
    	\begin{itemize}
    		\item Benchmarked the site with estimations of peak traffic and growth
    	 	\item Provisioned and hardened servers with redundancies
    	 	\item Automated deployments
    	 	\item Automated local development environments in Docker
    	 	\item Integrated and customized external services and API's
    	 	\item Heavily customized multi-source inventory and order splitting
    	 	\item Improved page performance and accessibility
    	 	\item Code reviewed and QA'd contractor commits
    	 	\item Introduced and managed task tracking, sprint planning, and sprint reviews which were eventually adopted by the rest of the company
    	 \end{itemize}
    	 In short, I played the roles of Ops, DevOps, Backend Dev, Frontend Dev, QA, Product Manager, and Project Manager.
    
 
 
\section{EXPERIENCE}
   \vspace{-0.1in}
   
   \begin{tabbing}
   		\hspace{2.0in}\= \hspace{2.7in}\= \kill % set up two tab positions
    	\textbf{Web Developer} \>Monrovia Nuresery Company \>Feb. 2020 - Present\\
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   
    Stack: \\
	Linux, PHP, Magento 2, Magneto Cloud, Git, JS, HTML, CSS (Less), MySQL, Bash, Docker, Klevu, Yotpo, Jira \\
	\\
	Minor Experience: \\
	Linux Mint, Redis, Elastic Search, Java, Python, Varnish, AWS, C\#, NCR Counterpoint, Clickup \\
	\\
	Role: \\
	\vspace{-0.15in}	
	\begin{itemize}
		\item Brought in to the company with its purchase of Plantt as the sole developer to maintain its operations including Java API's and a C\# Windows application.
		\item Moved full time to the monrovira.com website and focused on a heavily customized multi-source inventory implenation, Oracle ERP integrations, service integrations and customizations, performance enhancements, and accesibility imporovements.
	\end{itemize}

   \begin{tabbing}
   		\hspace{2.0in}\= \hspace{2.7in}\= \kill % set up two tab positions
    	\textbf{Web Developer} \>Plantt \>July 2019 - Feb. 2020\\
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   
    Stack: \\
	Linux, PHP, Magento 2, Magneto Cloud, Git, JS, HTML, CSS (Less), MySQL, Bash, Docker \\
	\\
	Minor Experience: \\
	Linux Mint, Redis, Elastic Search \\
	\\
	Role: \\
	\vspace{-0.15in}	
	\begin{itemize}
		\item Structuring, building, and maintaining a cohesive SaaS storefront on the Magento Cloud.
	\end{itemize}
   
   \begin{tabbing}
   		\hspace{2.0in}\= \hspace{2.7in}\= \kill % set up two tab positions
    	\textbf{Web Developer} \>Briteskies     \>May 2017 - July 2019\\
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   
    Stack: \\
	Linux, PHP, Magento 2, Magento 1, Git, JS, HTML, CSS (Less), MySQL, Bash, Docker \\
	\\
	Minor Experience: \\
	Linux Mint, CentOS, Redis, Elastic Search, Varnish, cPanel \\
	\\
	Role: \\
	\vspace{-0.15in}	
	\begin{itemize}
		\item Worked with legacy sites and then grew up into a more DevOps role, building pipelines, environments and utilities to aid the development, QA, and deployment processes.
		\item Built modules and fixed bugs in the full Magento 2 stack.
	\end{itemize}
    
   
   \begin{tabbing}
   		\hspace{2.0in}\= \hspace{2.7in}\= \kill % set up two tab positions
    	\textbf{Web Developer} \>BuyerQuest/Punchout Catalogs     \>Feb. 2011 - April 2017\\
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   
    Stack: \\
	Linux, PHP, Magento 1, Git, JS (jQuery, Grunt), HTML, CSS (Sass), MySQL, MongoDB \\
	\\
	Minor Experience: \\
	Linux Mint, Bash, Docker, Vagrant, Solr, Redis, Jenkins, Watson AI Services \\
	\\
	Role: \\
	\vspace{-0.15in}	
	\begin{itemize}
		\item Grew with the company from under 10 employees, while wearing many hats.
		\item Developed for the full stack, building out dozens of custom modules directly for clients.
		\item Was the sole developer, QA, and maintainer of a punchout gateway which has been responsible for handling over 3 billion dollars worth of orders to date.
		\item Led teams on up to 6 concurrent clients' projects, being responsive to urgent needs while balancing long-term coding goals of the core software.
	\end{itemize}
	
	
	\begin{tabbing}
		\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
		\textbf{Web Development Intern} \>Group NJI New Media \> July - Dec. 2010 \\
   \end{tabbing}\vspace{-20pt}
   
    Stack: \\
	Windows, Asp.net 4.0, C\#, Source Control, JS, HTML, CSS \\
	\\
	Role: \\
	\vspace{-0.15in}
	\begin{itemize}
		\item Worked on political sites building out forms, applying new design work, and integrating with external services like MailChimp and Facebook.
	\end{itemize}
	
	
	
\section{EDUCATION}
    \textbf{BS Software Development}, November 2010 \\
    Bellevue University \\    
    GPA: 4.0 \\  
    \\
    \textbf{BA Psychology}, May 2009 \\
    Kent State University \\    
    GPA: 3.94
	
	
\section{SOURCE}
	The LaTeX source code for this resume is available on GitHub at: \\
	\url{https://github.com/SamRogal/Resume}
 
\end{resume}
\end{document}